Applications of limited information strategies in Menger's game

### 2016-11-17 articles/applications-of-limited-information-strategies-in-mengers-game/article.tex
add keyword
partial revisions

\usepackage{tikz}
\usetikzlibrary{matrix}

@@

\keywords{Menger's property, Menger's game, limited information strategies}

@@

\begin{definition}
  A \(k\)-tactical strategy for a game \(G\) with moveset \(M\) is a function
  \(\sigma:M^{\leq k}\to M\); intuitively, it is a strategy which only considers
  the previous \(k\) moves of the opponent. If a winning \(k\)-tactical strategy
  exists for \(\pl P\) in the game \(G\), then we write \(\pl P\ktactwin{k} G\).
\end{definition}

\begin{definition}
  A \(k\)-Markov strategy for a game \(G\) with moveset \(M\) is a function
  \(\sigma:M^{\leq k}\times\omega\to M\); intuitively, it is a strategy which
  only considers the previous \(k\) moves of the opponent and the round number.
  If a winning \(k\)-Markov strategy exists for
  \(\pl P\) in the game \(G\), then we write \(\pl P\kmarkwin{k} G\).
\end{definition}

@@

\begin{proof}
  Let \(\sigma\) be a winning \((k+2)\)-mark. We define the \(2\)-mark \(\tau\) as
  follows:
    \[
      \tau(\<\mc U\>,0)
        =
      \bigcup_{m<k+2}
        \sigma(\<\underbrace{\mc U,\dots,\mc U}_{m+1}\>,m)
    \]
    \[
      \tau(\<\mc U,\mc V\>,n+1)
        =
      \bigcup_{m<k+2}
        \sigma(\<
          \underbrace{\mc U,\dots,\mc U}_{k+1-m},
          \underbrace{\mc V,\dots,\mc V}_{m+1}
        \>,(n+1)(k+2)+m)
    \]

  Let \(\<\mc U_0,\mc U_1,\dots\>\) be an attack by \(\pl C\) against \(\tau\).
  Then consider the attack
    \[
      \<
        \underbrace{\mc U_0,\dots,\mc U_0}_{k+2},
        \underbrace{\mc U_1,\dots,\mc U_1}_{k+2},
        \dots
      \>
    \]
  by \(\pl C\) against \(\sigma\). Since \(\sigma\) is a winning \((k+2)\)-mark,
    \[
      X
        =
      \bigcup_{m<k+2}
        \sigma(\<\underbrace{\mc U_0,\dots,\mc U_0}_{m+1}\>,m)
      \cup
      \bigcup_{n<\omega}
      \bigcup_{m<k+2}
        \sigma(\<
          \underbrace{\mc U_n,\dots,\mc U_n}_{k+1-m},
          \underbrace{\mc U_{n+1},\dots,\mc U_{n+1}}_{m+1}
        \>,(n+1)(k+2)+m)
    \]
    \[
      =
      \tau(\<\mc U_0\>,0)
      \cup
      \bigcup_{n<\omega}
      \tau(\<\mc U_n,\mc U_{n+1}\>,n+1)
    \]
  Thus \(\tau\) is a winning \(2\)-mark.
\end{proof}

@@

\begin{definition}
  For any cardinal \(\kappa\), let \(\oneptlind\kappa=\kappa\cup\{\infty\}\) denote
  the \term{one-point Lindel\"of-ication} of discrete \(\kappa\), where points in
  \(\kappa\) are isolated, and the neighborhoods of \(\infty\) are the co-countable
  sets containing it.
\end{definition}

One may prove directly that
  \(\pl F \notmarkwin \menGame{\oneptlind{\omega_1}}\)
without much effort; however, we postpone stating this until we have
shown that being Markov Menger is equivalent to being \(\sigma\)-compact
in regular spaces. Likewise, we postpone proving
  \(\pl F \kmarkwin2 \menGame{\oneptlind{\omega_1}}\)
in order to consider an equivalent set-theoretic game.

@@

In \(\menGame{\oneptlind\kappa}\), \(\pl C\) essentially chooses a countable set
to not include in her neighborhood of \(\infty\), followed by \(\pl F\) choosing
a finite subset of this complement to cover during each round. Thus,
\(\pl F\) need only be concerned with the \textit{intersection} of the
countable sets chosen by \(\pl C\) in \(\menGame{\oneptlind\kappa}\), rather
than the union as in \(\schFillStrictGame\kappa\).

Another difference between these games:
Scheepers required that \(\pl C\) always choose strictly
growing countable sets. If the goal is to study tactics,
then \(\pl C\) cannot be allowed to trap \(\pl F\) in a loop by
repeating the same
moves. But by eliminating this requirement, the study can then turn to Markov
strategies, bringing the game further in line with the Menger game played upon
\(\oneptlind\kappa\).

We introduce a few games to make the relationship between Scheeper's
\(\schFillStrictGame\kappa\) and \(\menGame{\oneptlind\kappa}\) more precise.

@@

\begin{figure}[h]
\begin{center}
\begin{tikzpicture}
  \matrix (m) [matrix of math nodes,row sep=3em,column sep=1em,minimum width=2em]
  {
    \pl F \kmarkwin{k+1}\menGame{\oneptlind\kappa} &
    \pl F \kmarkwin{k+1}\schFillIntGame\kappa \\

    \pl F \kmarkwin{k+1}\schFillInitialGame\kappa &
    \pl F \kmarkwin{k+1}\schFillGame\kappa \\

    &
    \pl F \ktactwin{k+1}\schFillStrictGame\kappa \\
  };
  \path[>=latex,->]
    (m-1-1) edge (m-2-1)
    (m-1-2) edge (m-2-2)
    (m-3-2) edge (m-2-2);
  \path[>=latex,<->]
    (m-1-1) edge (m-1-2)
    (m-2-1) edge (m-2-2);
\end{tikzpicture}
\end{center}
\caption{Diagram of Scheepers/Menger game implications}
\label{GamesDiagram}
\end{figure}

@@

\begin{proof}
  \(\pl F \kmarkwin{k+1}\menGame{\oneptlind\kappa}
    \Rightarrow
  \pl F \kmarkwin{k+1}\schFillIntGame\kappa\):
  Let \(\sigma\) be a winning \(k\)-mark for \(\pl F\) in
  \(\menGame{\oneptlind\kappa}\). Let \(\mc U(C)\) (resp. \(\mc U(s)\)) convert each
  countable subset \(C\) of \(\kappa\) (resp. finite sequence \(s\) of such subsets)
  into the open cover \([C]^1\cup\{\oneptlind\kappa\setminus C\}\)
  (resp. finite sequence of such open covers). Then \(\tau\) defined by
    \[
      \tau(s\concat\<C\>,n)
        =
      C\cap\sigma(\mc U(s\concat\<C\>),n)
    \]
  is a winning \((k+1)\)-mark for \(\pl F\) in \(\schFillIntGame\kappa\).

  \(\pl F \kmarkwin{k+1}\schFillIntGame\kappa
    \Rightarrow
  \pl F \kmarkwin{k+1}\menGame{\oneptlind\kappa}\):
  Let \(\sigma\) be a winning \(k\)-mark for \(\pl F\) in
  \(\schFillIntGame\kappa\). Let \(C(\mc U)\) (resp. \(C(s)\)) convert each open
  cover \(\mc U\) of \(\oneptlind\kappa\) (resp. finite sequence \(s\) of such covers)
  into a countable set \(C\) which is the complement of some neighborhood of
  \(\infty\) in \(\mc U\) (resp. finite sequence of such countable sets).
  Then \(\tau\) defined by
    \[
      \tau(s\concat\<\mc U\>,n)
        =
      (\oneptlind\kappa\setminus C(\mc U))
        \cup
      \sigma(C(s\concat\<\mc U)\>),n)
    \]
  is a winning \((k+1)\)-mark for \(\pl F\) in \(\menGame{\oneptlind\kappa}\).

  \(\pl F \kmarkwin{k+1}\schFillIntGame\kappa
    \Rightarrow
  \pl F \kmarkwin{k+1}\schFillInitialGame\kappa\):
  Let \(\sigma\) be a winning \(k\)-mark for \(\pl F\) in
  \(\schFillIntGame\kappa\). \(\sigma\) is also a winning \(k\)-mark for \(\pl F\)
  in \(\schFillInitialGame\kappa\).

  \(\pl F \kmarkwin{k+1}\schFillInitialGame\kappa
    \Rightarrow
  \pl F \kmarkwin{k+1}\schFillGame\kappa\): Let \(\sigma\) be a winning \(k\)-mark for \(\pl F\) in
  \(\schFillInitialGame\kappa\). For each finite sequence \(s\), let \(t\preceq s\) mean \(t\)
  is a final subsequence of \(s\). Then \(\tau\) defined by
    \[
      \tau(s\concat\<C\>,n)
        =
      \bigcup_{t\preceq s, m\leq n}
      \sigma(t\concat\<C\>,m)
    \]
  is a winning \((k+1)\)-mark for \(\pl F\) in \(\schFillGame\kappa\).

  \(\pl F \kmarkwin{k+1}\schFillGame\kappa
    \Rightarrow
  \pl F \kmarkwin{k+1}\schFillInitialGame\kappa\):
  Let \(\sigma\) be a winning \(k\)-mark for \(\pl F\) in
  \(\schFillGame\kappa\). \(\sigma\) is also a winning
  \((k+1)\)-mark for \(\pl F\)
  in \(\schFillInitialGame\kappa\).

  \(\pl F \ktactwin{k+1}\schFillStrictGame\kappa
    \Rightarrow
  \pl F \kmarkwin{k+1}\schFillGame\kappa\):
  Let \(\sigma\) be a winning \(k\)-tactic for \(\pl F\) in
  \(\schFillStrictGame\kappa\). For each countable subset \(C\) of \(\kappa\), let \(C+n\)
  be the union of \(C\) with the \(n\) least ordinals in \(\kappa\setminus C\).
  Then \(\tau\) defined by
    \[
      \tau(\<C_0,\dots,C_i\>,n)
        =
      \sigma(\<C_0+(n-i),\dots,C_i+n\>)
    \]
  is a winning \((k+1)\)-mark for \(\pl F\) in \(\schFillGame\kappa\).
\end{proof}

@@

Scheepers went on to show that \(\alcompS\kappa\) implies
\(\pl F \ktactwin2 \schFillStrictGame\kappa\). This proof, along with the following
facts, give us inspiration for
finding a winning \(2\)-Markov strategy in the Menger game played on
\(\oneptlind\kappa\).

@@

\begin{figure}[h]
\begin{center}
\begin{tikzpicture}
  \matrix (m) [matrix of math nodes,row sep=3em,column sep=1em,minimum width=2em]
  {
    &
    \pl F \kmarkwin2\menGame{\oneptlind\kappa} &
    \pl F \kmarkwin2\schFillIntGame\kappa \\

    \alcompS\kappa &
    \pl F \kmarkwin2\schFillInitialGame\kappa &
    \pl F \kmarkwin2\schFillGame\kappa \\

    &
    &
    \pl F \ktactwin2\schFillStrictGame\kappa \\
  };
  \path[>=latex,->]
    (m-2-1) edge (m-1-2)
    (m-2-1) edge (m-2-2)
    (m-2-1) edge (m-3-3)
    (m-1-2) edge (m-2-2)
    (m-1-3) edge (m-2-3)
    (m-3-3) edge (m-2-3);
  \path[>=latex,<->]
    (m-1-2) edge (m-1-3)
    (m-2-2) edge (m-2-3);
\end{tikzpicture}
\end{center}
\caption{Diagram of Scheeper/Menger game implications with \(\alcompS\kappa\)}
\label{GamesDiagram2}
\end{figure}

@@

  Let \(f_A\) for \(A\in[\kappa]^{\leq\omega}\) witness \(\alcompS\kappa\). We define
  the \(2\)-mark \(\sigma\) as follows:
    \[
      \sigma(\<A\>,0) = \{\alpha\in A: f_A(\alpha) \leq 0 \}
    \]
    \[
      \sigma(\<A,B\>,n+1)
        =
      \{
        \alpha \in A\cap B
      :
        f_B(\alpha) \leq n+1 \text{ or }
        f_A(\alpha)\not=f_B(\alpha)
      \}
    \]
  For any attack \(\<A_0,A_1,\dots\>\) by \(\pl C\) and
  \(\alpha\in\bigcap_{n<\omega}A_n\), either \(f_{A_n}(\alpha)\) is constant for
  all \(n\), or \(f_{A_n}(\alpha)\not=f_{A_{n+1}}(\alpha)\) for some \(n\);
  either way, \(\alpha\) is covered.
\end{proof}

\begin{corollary}
  \(\pl F \kmarkwin2\menGame{\oneptlind\omega_1}\).
\end{corollary}

@@

     \text{Markov Menger} &
     2\text{-Markov Menger} &
     \text{Strategic Menger} &
     \text{Menger} \\
  };
  \path[>=latex,<->]
    (m-1-1) edge (m-2-1)
    (m-1-2) edge (m-2-2)
    (m-1-3) edge (m-2-3)
    (m-1-4) edge (m-2-4);
  \path[>=latex,->]
    (m-1-1) edge (m-1-2)
    (m-2-1) edge (m-2-2)
    (m-1-2) edge (m-1-3)
    (m-2-2) edge (m-2-3)
    (m-1-3) edge (m-1-4)
    (m-2-3) edge (m-2-4);
  \path[>=latex,->,bend right=30, dotted]
    (m-1-2) edge node {\( \not \)} (m-1-1)
    (m-2-2) edge node {\( \not \)} (m-2-1)
    (m-1-4) edge node {\( \not \)} (m-1-3)
    (m-2-4) edge node {\( \not \)} (m-2-3);
  \path[>=latex,->,bend right=30, dotted]
    (m-1-3) edge node {\( ? \)} (m-1-2)
    (m-2-3) edge node {\( ? \)} (m-2-2);
\end{tikzpicture}
\end{center}
\caption{Diagram of covering properties related to the Menger game}
\label{menSpec}
\end{figure}

@@

\begin{corollary}
  \(\pl F\notmarkwin\menGame{\oneptlind{\omega_1}}\).
\end{corollary}

@@

  So if \(\mc U_t\) is a basic open cover for \(t<s\in\omega^{<\omega}\), and
  \(\mc V\) is any basic open cover, we may choose a finite subcollection
  \(\mc F(s,\mc V)\) of \(\mc V\) such that
  \[
    \sigma(\<\mc U_{s\rest 1},\dots,\mc U_{s},\mc V\>)
      \subseteq
    \bigcup \mc F(s,\mc V)
  \]

@@

  Let \(t:\omega\to\omega^{<\omega}\) be a bijection. We define the Markov
  strategy \(\tau\) as follows:
  \[
    \tau(\<\mc V\>, n)
      =
    \bigcup \mc F(t(n),\mc V)
  \]

  Suppose there exists a counter-attack \(\<\mc V_0,\mc V_1,\dots\>\) of
  basic open covers which defeats \(\tau\). Then there exists
  \(f:\omega\to\omega\) such that, letting \(t(m_n)=f\rest n\):
  \[
    \begin{array}{rcl}
    x & \not\in & \tau(\<\mc V_{m_n}\>,m_n) \\
    & = & \bigcup\mc F(f\rest n,\mc V_{m_n}) \\
    & = & \bigcup\mc F(f\rest n,\mc U_{f\rest (n+1)}) \\
    & \supseteq & \sigma(\<\mc U_{f\rest 1},\dots,\mc U_{f\rest(n+1)}\>)
    \end{array}
  \]

@@

\begin{definition}
  A subset \(Y\) of \(X\) is \term{relatively robustly Menger} if there exist
  functions \(r_{\mc V}:Y\to\omega\)
  for each open cover \(\mc V\) of \(X\) such that
  for all open covers \(\mc U,\mc V\) and numbers \(n<\omega\),
  the following sets are \(\mc V\)-finite:
    \[
      c(\mc V,n)=\{ x\in Y : r_{\mc V}(x)\leq n\}
    \]
    \[
      p(\mc U,\mc V,n+1)=\{ x\in Y : n<r_{\mc U}(x)<r_{\mc V}(x)\}
    \]
\end{definition}

>>>>

\usepackage{tikz}
\usetikzlibrary{matrix}
\usetikzlibrary{arrows}

@@

\keywords{Menger property, Menger game, \(\sigma\)-compact spaces,
limited information strategies}

@@

\begin{definition}
  A \(k\)-tactical strategy for a game \(G\) with moveset \(M\) is a function
  \(\sigma:M^{\leq k}\to M\); intuitively, it is a strategy which only considers
  the previous \(k\) or less moves of the opponent \(t\in M^{\leq k}\), and yields
  the appropriate move \(\sigma(t)\) for the player using it.
  If a winning \(k\)-tactical strategy
  exists for \(\pl P\) in the game \(G\), then we write \(\pl P\ktactwin{k} G\).
\end{definition}

\begin{definition}
  A \(k\)-Markov strategy for a game \(G\) with moveset \(M\) is a function
  \(\sigma:M^{\leq k}\times\omega\to M\); intuitively, it is a strategy which
  only considers the previous \(k\) or less moves of the opponent
  \(t\in M^{\leq k}\) and the round number \(n<\omega\),
  and yields the appropriate move \(\sigma(t,n)\) for the player using it.
  If a winning \(k\)-Markov strategy exists for
  \(\pl P\) in the game \(G\), then we write \(\pl P\kmarkwin{k} G\).
\end{definition}

@@

\begin{proof}
  Let \(\sigma\) be a winning \((k+2)\)-mark. We define the \(2\)-mark \(\tau\) as
  follows:
    \[
      \tau(\<\mc U\>,0)
        =
      \bigcup_{m<k+2}
        \sigma(\<\underbrace{\mc U,\dots,\mc U}_{m+1}\>,m)
    ,\]
    \[
      \tau(\<\mc U,\mc V\>,n+1)
        =
      \bigcup_{m<k+2}
        \sigma(\<
          \underbrace{\mc U,\dots,\mc U}_{k+1-m},
          \underbrace{\mc V,\dots,\mc V}_{m+1}
        \>,(n+1)(k+2)+m)
    .\]

  Let \(\<\mc U_0,\mc U_1,\dots\>\) be an attack by \(\pl C\) against \(\tau\).
  Then consider the attack
    \[
      \<
        \underbrace{\mc U_0,\dots,\mc U_0}_{k+2},
        \underbrace{\mc U_1,\dots,\mc U_1}_{k+2},
        \dots
      \>
    \]
  by \(\pl C\) against \(\sigma\). Since \(\sigma\) is a winning \((k+2)\)-mark,
    \[
      X
        =
      \bigcup_{m<k+2}
        \sigma(\<\underbrace{\mc U_0,\dots,\mc U_0}_{m+1}\>,m)
      \cup
      \bigcup_{n<\omega}
      \bigcup_{m<k+2}
        \sigma(\<
          \underbrace{\mc U_n,\dots,\mc U_n}_{k+1-m},
          \underbrace{\mc U_{n+1},\dots,\mc U_{n+1}}_{m+1}
        \>,(n+1)(k+2)+m)
    \]
    \[
      =
      \tau(\<\mc U_0\>,0)
      \cup
      \bigcup_{n<\omega}
      \tau(\<\mc U_n,\mc U_{n+1}\>,n+1)
    .\]
  Thus \(\tau\) is a winning \(2\)-mark. Of course, it is trivial to
  define a winning \((k+2)\)-mark from a \(2\)-mark by simply ignoring
  the extra \(k\) moves.
\end{proof}

@@

\begin{definition}
  For any cardinal \(\kappa\), let \(\onePtLind\kappa=\kappa\cup\{\infty\}\) denote
  the \term{one-point Lindel\"of-ication} of discrete \(\kappa\), where points in
  \(\kappa\) are isolated, and the neighborhoods of \(\infty\) are the co-countable
  sets containing it.
\end{definition}

One may prove directly that
  \(\pl F \notmarkwin \menGame{\onePtLind{\omega_1}}\)
without much effort; however, we postpone stating this until we have
shown that being Markov Menger is equivalent to being \(\sigma\)-compact
in regular spaces. Likewise, we postpone proving
  \(\pl F \kmarkwin2 \menGame{\onePtLind{\omega_1}}\)
in order to consider an equivalent set-theoretic game.

@@

In \(\menGame{\onePtLind\kappa}\), \(\pl C\) essentially chooses a countable set
to not include in her neighborhood of \(\infty\), followed by \(\pl F\) choosing
a finite subset of this complement to cover during each round. Thus,
\(\pl F\) need only be concerned with the \textit{intersection} of the
countable sets chosen by \(\pl C\) in \(\menGame{\onePtLind\kappa}\), rather
than the union as in \(\schFillStrictGame\kappa\).

Another difference between these games:
Scheepers required that \(\pl C\) always choose strictly
growing countable sets. If the goal is to study tactics,
then \(\pl C\) cannot be allowed to trap \(\pl F\) in a loop by
repeating the same
moves. But by eliminating this requirement, the study can then turn to Markov
strategies, bringing the game further in line with the Menger game played upon
\(\onePtLind\kappa\).

We introduce a few games to make the relationship between Scheeper's
\(\schFillStrictGame\kappa\) and \(\menGame{\onePtLind\kappa}\) more precise.

@@

% \begin{figure}[h]
% \begin{center}
% \begin{tikzpicture}
%   \matrix (m) [matrix of math nodes,row sep=3em,column sep=1em,minimum width=2em]
%   {
%     \pl F \kmarkwin{k+1}\menGame{\onePtLind\kappa} &
%     \pl F \kmarkwin{k+1}\schFillIntGame\kappa \\
%
%     \pl F \kmarkwin{k+1}\schFillInitialGame\kappa &
%     \pl F \kmarkwin{k+1}\schFillGame\kappa \\
%
%     &
%     \pl F \ktactwin{k+1}\schFillStrictGame\kappa \\
%   };
%   \path[>=latex,->]
%     (m-1-1) edge (m-2-1)
%     (m-1-2) edge (m-2-2)
%     (m-3-2) edge (m-2-2);
%   \path[>=latex,<->]
%     (m-1-1) edge (m-1-2)
%     (m-2-1) edge (m-2-2);
% \end{tikzpicture}
% \end{center}
% \caption{Diagram of Scheepers/Menger game implications}
% \label{GamesDiagram}
% \end{figure}

\begin{figure}[ht]
\begin{center}
\begin{tikzpicture}[x=0.8in,y=0.5in]
% \node at (-3.5,2) {\(\alcompS\kappa\)};
\node at (-3.5,0) {\(\pl F \ktactwin{(k+1)}\schFillStrictGame\kappa\)};
% \node at (0,2) {\(\alcompSP\kappa\)};
\node at (-1.1,1) {\(\pl F \kmarkwin{(k+1)}\menGame{\onePtLind\kappa}\)};
\node at (0,1) {\(\Leftrightarrow\)};
\node at (1,1) {\(\pl F \kmarkwin{(k+1)}\schFillIntGame\kappa\)};
\node at (-1,0) {\(\pl F \kmarkwin{(k+1)}\schFillInitialGame\kappa\)};
\node at (0,0) {\(\Leftrightarrow\)};
\node at (1,0) {\(\pl F \kmarkwin{(k+1)}\schFillGame\kappa\)};
\node at (0,-1) {\(\pl F \kmarkwin{(k+1)}\schFillStrictGame\kappa\)};
% \draw[-implies,double equal sign distance] (-3.2,2) -- (-0.3,2);
\draw[-implies,double equal sign distance] (-2.5,0) -- (-2,0);
% \draw[-implies,double equal sign distance] (-3.5,1.65) -- (-3.5,0.35);
% \draw[-implies,double equal sign distance] (0,1.65) -- (0,1.35);
\draw[-implies,double equal sign distance] (0,0.65) -- (0,0.35);
\draw[-implies,double equal sign distance] (0,-0.35) -- (0,-0.65);
\end{tikzpicture}
\end{center}
\caption{Diagram of Scheeper/Menger game implications}% with \(\alcompS{\kappa},\alcompS{\kappa}\)}
\label{GamesDiagram}
\end{figure}

@@

\begin{proof}
  \(\pl F \kmarkwin{(k+1)}\menGame{\onePtLind\kappa}
    \Rightarrow
  \pl F \kmarkwin{(k+1)}\schFillIntGame\kappa\):
  Let \(\sigma\) be a winning \((k+1)\)-mark for \(\pl F\) in
  \(\menGame{\onePtLind\kappa}\). Let \(\mc U(C)\) (resp. \(\mc U(s)\)) convert each
  countable subset \(C\) of \(\kappa\) (resp. finite sequence \(s\) of such subsets)
  into the open cover \([C]^1\cup\{\onePtLind\kappa\setminus C\}\)
  (resp. finite sequence of such open covers). Then \(\tau\) defined by
    \[
      \tau(s\concat\<C\>,n)
        =
      C\cap\sigma(\mc U(s\concat\<C\>),n)
    \]
  is a winning \((k+1)\)-mark for \(\pl F\) in \(\schFillIntGame\kappa\).

  \(\pl F \kmarkwin{(k+1)}\schFillIntGame\kappa
    \Rightarrow
  \pl F \kmarkwin{(k+1)}\menGame{\onePtLind\kappa}\):
  Let \(\sigma\) be a winning \((k+1)\)-mark for \(\pl F\) in
  \(\schFillIntGame\kappa\). Let \(C(\mc U)\) (resp. \(C(s)\)) convert each open
  cover \(\mc U\) of \(\onePtLind\kappa\) (resp. finite sequence \(s\) of such covers)
  into a countable set \(C\) which is the complement of some neighborhood of
  \(\infty\) in \(\mc U\) (resp. finite sequence of such countable sets).
  Then \(\tau\) defined by
    \[
      \tau(s\concat\<\mc U\>,n)
        =
      (\onePtLind\kappa\setminus C(\mc U))
        \cup
      \sigma(C(s\concat\<\mc U\>),n)
    \]
  is a winning \((k+1)\)-mark for \(\pl F\) in \(\menGame{\onePtLind\kappa}\).

  \(\pl F \kmarkwin{(k+1)}\schFillIntGame\kappa
    \Rightarrow
  \pl F \kmarkwin{(k+1)}\schFillInitialGame\kappa\):
  Let \(\sigma\) be a winning \((k+1)\)-mark for \(\pl F\) in
  \(\schFillIntGame\kappa\). \(\sigma\) is also a winning \((k+1)\)-mark for \(\pl F\)
  in \(\schFillInitialGame\kappa\).

  \(\pl F \kmarkwin{(k+1)}\schFillInitialGame\kappa
    \Rightarrow
  \pl F \kmarkwin{(k+1)}\schFillGame\kappa\): Let \(\sigma\) be a winning
  \((k+1)\)-mark for \(\pl F\) in
  \(\schFillInitialGame\kappa\). For each finite sequence \(s\), let
  \(t\preceq s\) mean \(t\)
  is a final subsequence of \(s\). Then \(\tau\) defined by
    \[
      \tau(s\concat\<C\>,n)
        =
      \bigcup_{t\preceq s, m\leq n}
      \sigma(t\concat\<C\>,m)
    \]
  is a winning \((k+1)\)-mark for \(\pl F\) in \(\schFillGame\kappa\),
  considering that \(\sigma\) ensures that \(C_n\) is covered when
  attacked by \(\<C_n,C_{n+1},\dots\>\) for all \(n<\omega\).

  \(\pl F \kmarkwin{(k+1)}\schFillGame\kappa
    \Rightarrow
  \pl F \kmarkwin{(k+1)}\schFillInitialGame\kappa\):
  Let \(\sigma\) be a winning \((k+1)\)-mark for \(\pl F\) in
  \(\schFillGame\kappa\). \(\sigma\) is also a winning
  \((k+1)\)-mark for \(\pl F\)
  in \(\schFillInitialGame\kappa\).

  \(\pl F \ktactwin{(k+1)}\schFillStrictGame\kappa
    \Rightarrow
  \pl F \kmarkwin{(k+1)}\schFillGame\kappa\):
  Let \(\sigma\) be a winning \((k+1)\)-tactic for \(\pl F\) in
  \(\schFillStrictGame\kappa\). For each countable subset \(C\) of \(\kappa\), let \(C+n\)
  be the union of \(C\) with the \(n\) least ordinals in \(\kappa\setminus C\).
  Then for every valid attack \(\<C_0,C_1,C_2,\dots\>\) by \(\pl C\) in
  \(\schFillGame\kappa\), it follows that \(\<C_0,C_1+1,C_2+2,\dots\>\) is a
  valid attack by \(\pl C\) in \(\schFillStrictGame\kappa\) as
  \(C_{n+1}\supseteq C_n\) ensures that
  \(C_{n+1}+(n+1)\) includes all the \(n\) added elements in \(C_n+n\)
  in addition to at least one more.
  Thus \(\tau\) defined by
    \[
      \tau(\<C_n,\dots,C_{n+i}\>,n+i)
        =
      \sigma(\<C_n+n,\dots,C_{n+i}+(n+i)\>)
    \]
  is a winning \((k+1)\)-mark for \(\pl F\) in \(\schFillGame\kappa\),
  considering that \(\sigma\) ensures that
  \(\bigcup_{n<\omega}(C_n+n)\supseteq\bigcup_{n<\omega}C_n\)
  is covered when attacked by \(\<C_0,C_1+1,C_2+2,\dots\>\).

  \(\pl F \kmarkwin{(k+1)}\schFillGame\kappa
    \Rightarrow
  \pl F \kmarkwin{(k+1)}\schFillStrictGame\kappa\):
  Let \(\sigma\) be a winning \((k+1)\)-mark for \(\pl F\) in
  \(\schFillGame\kappa\). \(\sigma\) is also a winning
  \((k+1)\)-mark for \(\pl F\)
  in \(\schFillStrictGame\kappa\).
\end{proof}

@@

Scheepers went on to show that \(\alcompS\kappa\) implies
\(\pl F \ktactwin2 \schFillStrictGame\kappa\). This proof, along with the following
facts, give us inspiration for
finding a winning \(2\)-Markov strategy in the Menger game played on
\(\onePtLind\kappa\).

@@

\begin{figure}[ht]
\begin{center}
\begin{tikzpicture}[x=0.8in,y=0.5in]
\node at (-3.5,1) {\(\alcompS\kappa\)};
\node at (-3.5,0) {\(\pl F \ktactwin2\schFillStrictGame\kappa\)};
% \node at (0,2) {\(\alcompSP\kappa\)};
\node at (-1,1) {\(\pl F \kmarkwin2\menGame{\onePtLind\kappa}\)};
\node at (0,1) {\(\Leftrightarrow\)};
\node at (1,1) {\(\pl F \kmarkwin2\schFillIntGame\kappa\)};
\node at (-1,0) {\(\pl F \kmarkwin2\schFillInitialGame\kappa\)};
\node at (0,0) {\(\Leftrightarrow\)};
\node at (1,0) {\(\pl F \kmarkwin2\schFillGame\kappa\)};
\node at (0,-1) {\(\pl F \kmarkwin2\schFillStrictGame\kappa\)};
\draw[-implies,double equal sign distance] (-3.2,1) -- (-1.9,1);
\draw[-implies,double equal sign distance] (-2.6,0) -- (-1.9,0);
\draw[-implies,double equal sign distance] (-3.5,0.65) -- (-3.5,0.35);
% \draw[-implies,double equal sign distance] (0,1.65) -- (0,1.35);
\draw[-implies,double equal sign distance] (0,0.65) -- (0,0.35);
\draw[-implies,double equal sign distance] (0,-0.35) -- (0,-0.65);
\end{tikzpicture}
\end{center}
\caption{Diagram of Scheeper/Menger game implications}% with \(\alcompS{\kappa},\alcompS{\kappa}\)}
\label{GamesDiagram2}
\end{figure}

@@

  Let \(f_A\) for \(A\in[\kappa]^{\leq\omega}\) witness \(\alcompS\kappa\). We define
  the \(2\)-mark \(\sigma\) as follows:
    \[
      \sigma(\<A\>,0) = \{\alpha\in A: f_A(\alpha) \leq 0 \}
    \]
    \[
      \sigma(\<A,B\>,n+1)
        =
      \{
        \alpha \in A\cap B
      :
        f_B(\alpha) \leq n+1 \text{ or }
        f_A(\alpha)\not=f_B(\alpha)
      \}
    .\]
  For any attack \(\<A_0,A_1,\dots\>\) by \(\pl C\) and
  \(\alpha\in\bigcap_{n<\omega}A_n\), either \(f_{A_n}(\alpha)\) is constant for
  all \(n\), or \(f_{A_n}(\alpha)\not=f_{A_{n+1}}(\alpha)\) for some \(n\);
  either way, \(\alpha\) is covered.
\end{proof}

\begin{corollary}
  \(\pl F \kmarkwin2\menGame{\onePtLind\omega_1}\).
\end{corollary}

@@

     \text{Markov Menger} &
     2\text{-Markov Menger} &
     \text{Strategic Menger} &
     \text{Menger} \\
  };

  \draw[implies-implies,double equal sign distance]
    (m-1-1) -- (m-2-1);
  \draw[implies-implies,double equal sign distance]
    (m-1-2) -- (m-2-2);
  \draw[implies-implies,double equal sign distance]
    (m-1-3) -- (m-2-3);
  \draw[implies-implies,double equal sign distance]
    (m-1-4) -- (m-2-4);

  \draw[-implies,double equal sign distance]
    (m-1-1) -- (m-1-2);
  \draw[-implies,double equal sign distance]
    (m-2-1) -- (m-2-2);
  \draw[-implies,double equal sign distance]
    (m-1-2) -- (m-1-3);
  \draw[-implies,double equal sign distance]
    (m-2-2) -- (m-2-3);
  \draw[-implies,double equal sign distance]
    (m-1-3) -- (m-1-4);
  \draw[-implies,double equal sign distance]
    (m-2-3) -- (m-2-4);

  \draw[-implies,double equal sign distance,bend right=30]
    (m-1-2) -- node {\( \not \)} (m-1-1);
  \path[>=latex,->,bend right=30, dotted]
    (m-2-2) edge node {\( \not \)} (m-2-1)
    (m-1-4) edge node {\( \not \)} (m-1-3)
    (m-2-4) edge node {\( \not \)} (m-2-3);
  \path[>=latex,->,bend right=30, dotted]
    (m-1-3) edge node {\( ? \)} (m-1-2)
    (m-2-3) edge node {\( ? \)} (m-2-2);
\end{tikzpicture}
\end{center}
\caption{Diagram of covering properties related to the Menger game TODO FIX}
\label{menSpec}
\end{figure}

@@

\begin{corollary}
  \(\pl F\notmarkwin\menGame{\onePtLind{\omega_1}}\).
\end{corollary}

@@

  So if \(\mc U_t\) is a basic open cover for \(t<s\in\omega^{<\omega}\), and
  \(\mc V\) is any basic open cover, we may choose a finite subcollection
  \(\mc F(s,\mc V)\) of \(\mc V\) such that
  \[
    \sigma(\<\mc U_{s\rest 1},\dots,\mc U_{s},\mc V\>)
      \subseteq
    \bigcup \mc F(s,\mc V)
  .\]

@@

  Let \(t:\omega\to\omega^{<\omega}\) be a bijection. We define the Markov
  strategy \(\tau\) as follows:
  \[
    \tau(\<\mc V\>, n)
      =
    \bigcup \mc F(t(n),\mc V)
  .\]

  Suppose there exists a counter-attack \(\<\mc V_0,\mc V_1,\dots\>\) of
  basic open covers which defeats \(\tau\). Then there exists
  \(f:\omega\to\omega\) such that, letting \(t(m_n)=f\rest n\):
  \[
    \begin{array}{rcl}
    x & \not\in & \tau(\<\mc V_{m_n}\>,m_n) \\
    & = & \bigcup\mc F(f\rest n,\mc V_{m_n}) \\
    & = & \bigcup\mc F(f\rest n,\mc U_{f\rest (n+1)}) \\
    & \supseteq & \sigma(\<\mc U_{f\rest 1},\dots,\mc U_{f\rest(n+1)}\>)
    \end{array}
  .\]

@@

\begin{definition}
  A subset \(Y\) of \(X\) is \term{relatively robustly Menger} if there exist
  functions \(r_{\mc V}:Y\to\omega\)
  for each open cover \(\mc V\) of \(X\) such that
  for all open covers \(\mc U,\mc V\) and numbers \(n<\omega\),
  the following sets are \(\mc V\)-finite:
    \[
      c(\mc V,n)=\{ x\in Y : r_{\mc V}(x)\leq n\}
    ,\]
    \[
      p(\mc U,\mc V,n+1)=\{ x\in Y : n<r_{\mc U}(x)<r_{\mc V}(x)\}
    .\]
\end{definition}
